---
title: "glmplus"
author: "Lex Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`glmplus` is an enhanced version of general linear model for logistic regression. There are `summary.glmplus` and `plot.glmplus` in this package.

## summary.glmplus

`summary.glmplus` provides, in addition to the baseR `summary.glm`, odds ratio and confidence interval.
```{r summary, warning=F}
library(glmplus)
data(mtcars)
glm_model <- glmplus(vs ~ cyl + mpg + hp, data=mtcars, family=binomial)
summary(glm_model)
```

## plot.glmplus

`plot.glmplus` returns a ggplot object. The plot demonstrates the relationship between the given variable and the outcome binary variable.
```{r fig.height=4.5, fig.width=7}
library(glmplus)
data(mtcars)
glm_model <- glmplus(vs ~ cyl + mpg + hp, data=mtcars, family=binomial)
plot(glm_model, "hp")
```

```{r fig.height=4.5, fig.width=7}
plot(glm_model, "hp", "cyl")
```

```{r fig.height=4.5, fig.width=7}
plot(glm_model, "hp") + labs(y="Prob(V-shaped Engine)", 
                             x="Horsepower", 
                             title="Relationship of V-shape engine and horsepower",
                             subtitle="controlling for mpg and number of cylinders")
```


