---
title: "Multi Functions"
author: "Shane Ross"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Two-table verbs}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(multi_reg)
```

While base R's lm returns a very informative and useful multiple regression 
model, these functions produce dull tables and graphs and bury valuable 
regression information in lists. Developed to refine the lm functions, the 
multi functions (multi_reg and multi_plot) output the same information
returned by the lm functions, but present it in a much more aesthetically 
pleasing and clear way.

## Regression Results

While lm.summary presents regression results through a basic table, 
multi_reg depicts the results of the linear model through a visually appealing and highly comprehensible stargazer table.

```{r Multiple Regression Stargazer Table}
data(mtcars)
regression <- lm(mpg ~ wt + hp + cyl, data = mtcars)
multi_reg(regression, mtcars)
```

The multi_reg function also enhances the results table embedded in 
lm.summary by adding a 95% confidence interval for each coefficient as well
as stars to represent significant predictors.

```{r Multiple Regression Results}
a <- multi_reg(regression, mtcars)
a[["coefficients"]]
```

In order to facilitate user demands to immediately save the results of the 
multiple regression, the multi_reg function includes the `export_data`
parameter. When `export_data = TRUE`, this function will save the results
of the multiple regression model into an Excel file. The `file_name` 
parameter allows the user to customize the name of this Excel file.

## Regression Diagnostic Tests

Multiple linear regressions assume that residuals are normally distributed 
and that independent variables are not highly correlated with one another. 
While the lm function does not allow clear opportunities to assess these 
assumptions, multi_reg offers the user a histogram of the model's results as
well as a correlation plot depicting the correlations of each predictor in 
the model.

```{r Diagnostic Tests}
multi_reg(regression, mtcars, results = FALSE, 
          hist_of_resid = TRUE, corr_plot = TRUE)
```

## Regression Diagnostic Plots

Although the lm.plot function outputs extremely informative plots assessing
the validity of the multiple regression model, these plots are exceptionally
dull. In order to more persuasively and transparently convey these results, 
mulit_plot utilizes ggplot to return the same informaion in a more elegant 
fashion. Multi_plot also includes a Residuals versus Order plot to evaluate 
the relationship among the residuals over the duration of data collection.

```{r Diagnostic Plots}
multi_plot(regression, mtcars, wt)
```
