---
title: "plotROCS Function"
author: "Elizaveta Kravchenko"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The plotROCS function^[Some code for the generation of the plot and relevant statistics as queried by the hidden helper function `getProbs` have been used from "Enhanced ROC Curve" coding example curated by Professor Robert Kabacoff as part of QAC385: Advanced R. Citation: Original source unknown. Retrieved by Kabacoff, Robert. "code - enhanced ROC curve.R." Function. Wesleyan University. Middletown, CT. October 2018. Accessed 4 December, 2018] is a more detailed alternative to plotting logistic regression model ROC curves than using the ROC package. The function inputs one or more data models, and calculates a detailed ROC curve with user specified options. These options include line and plot color manipulation, generation of the optimal point on plot, and cutoff value displays. A table of important values for each model is printed to the console upon running; the values include the optimal cutoff point, model accuracy, sensitivity, specificity, and area under the curve. Plot dimensions depend on the "Plots" window size where graph is generated.

Note: The data sets for each model must be *unique*. Using models generated from the same data set (ex, `train`) will result in an error.

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Set Up and a Few Examples

There are two preprogrammed model examples available to this function; one using the regclass data set PIMA^[Retrieved from Course Moodle Page for QAC385: Advanced R. Kabacoff, Robert. "code - Logistic Regression 3.R." Code sample. Wesleyan University. Middletown, CT. October 2018. Accessed 4 December, 2018], and another utilizing Wisconsin Breast Cancer data^[Retrieved from Course Moodle Page for QAC385: Advanced R. Kabacoff, Robert. "code - Logistic Regression 2.R." Code sample. Wesleyan University. Middletown, CT. October 2018. Accessed 4 December, 2018].

```{r,warning=F, message=F}
library(plotROCS)
#PIMA
fit.glm <-model1()
#Breast Cancer
fit<-model2()
```

### Usage
**Simply input your models into the function. An example with all of the presets:**

```{r, warning=F, message=F,fig.show='hold'}
plotROCS(fit.glm, fit)
```

**An example changing the line and optimal point colors:**

```{r,fig.show='hold'}
plotROCS(fit.glm, fit, colorsList = c("purple","pink"), colorPoints = "green")
```

**An example changing the cutoff values, excluding the optimal points:**
```{r,fig.show='hold'}
plotROCS(fit.glm, colorsList = "cornflowerblue", opCP = F, cutoffSpec = seq(0,1,by=.25))
```

