---
title: "plotROCS Function"
author: "Elizaveta Kravchenko"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The plotROCS function is a more detailed alternative to plotting models than using the ROC package. The function inputs one or more data models, and calculates a detailed ROC curve with user specified options, which  include line and plot color manipulation, generation of the optimal point on plot, and cutoff value displays. A table of important values for each model is printed to the console; the values include the optimal cutoff point, model accuracy, sensitivity, specificity, and area under the curve.

Note: The data sets for each model must be *unique*. Using models generated from the same data set (ex, train) will result in an error.

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r, warning=F,message=F,echo=F}
# plot 1
if (!require("caret")) install.packages("caret")
if (!require("regclass")) install.packages("regclass")
library(caret)
library(regclass)
data("PIMA")
index <- createDataPartition(PIMA$Diabetes, p=0.7, list=FALSE)
train <- PIMA[index,]
test <- PIMA[-index,]
fit.glm <- glm(Diabetes ~ ., data=train, family = binomial)

# plot 2
loc <- "http://archive.ics.uci.edu/ml/machine-learning-databases/"
ds  <- "breast-cancer-wisconsin/breast-cancer-wisconsin.data"
url <- paste(loc, ds, sep="")

breast <- read.table(url, sep=",", header=FALSE, na.strings="?")
names(breast) <- c("ID", "clumpThickness", "sizeUniformity",
                   "shapeUniformity", "maginalAdhesion", 
                   "singleEpithelialCellSize", "bareNuclei", 
                   "blandChromatin", "normalNucleoli", "mitosis", "class")

df <- breast[-1]
df$class <- factor(df$class, levels=c(2,4), 
                   labels=c("benign", "malignant"))

index <- createDataPartition(breast$class, p=0.7, list=FALSE)
train1 <- df[index,]
test <- df[-index,]
fit <- glm(class ~ ., data=train1, family=binomial)
```

### Simply input your models into the function

```{r, warning=F}
library(plotROCS)
plotROCS(fit.glm, fit)
```
### Change the line and optimal point color

```{r}
plotROCS(fit.glm, fit, colorsList = c("purple","pink"), colorPoints = "green")
```

### Change the cutoff values, do not include the optimal points
```{r}
plotROCS(fit.glm, colorsList = "cornflowerblue", opCP = F, cutoffSpec = seq(0,1,by=.25))
```

